Subsegmental language detection in Celtic language text

### 2014-06-28 codeswitch-cltw-2014/codeswitch_camera_ready.tex
conclusions
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55051 72bbbca6-d526-0410-a7d9-f06f51895060
chunking re written .. pseducode needs to be added
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55052 72bbbca6-d526-0410-a7d9-f06f51895060

This section describes the heuristics taken into account while performing the chunking of the input data according to 
the sequences of segments in different languages.

A flag is set at the beginning of the input text, and this moves forward to the position in the text upto where confident 
chunking has been performed. For example, in case of a continuous prediction there would be no change and since the 
predicted tag of the new word corresponds to that already of the expanding chunk, this word is also included in the 
same chunk. In case of a doubt, the flag is set at the same position, and no final decision on labelling the word is 
performed, to have more confidence on the code-switch, the process moves on to the next token, if it corresponds to 
that of the previous chunk, then both these undecided words are labelled and included in the chunk, otherwise a change 
is noted and a new chunk is created with the changed label. In this process, we are trying to identify the sub-segments 
that we need, thus performing both tasks at once, the first being language prediction and second being the chunking decision.

@@

This paper has presented a very preliminary investigation into subsegment language identification in Celtic language texts. We have
proposed a model that chunks input text into segments and performs language identification on these segments at the same time. Precision and
recall are low, leaving a lot of room for further work. Some of our plans are as follows. We would like to annotate more test data,
at least 100 tweets in each language. We would also like to attempt our method using higher order character n-gram models for backoff, and
n-gram word language models for detection.

>>>>

This section describes the heuristics taken into account while performing the chunking of the input data according to 
the sequences of segments in different languages. 
'Chunks' represent the evaluated tuples of segments and their labelled language, buffer is the expanding segment.
 \textit{lang\_predict} corressponds to any function which is used to determine the language of the token. The flag 
variable helps in implementing the heuristic of minimum segment size while labelling chunks.

%A flag is set at the beginning of the input text, and this moves forward to the position in the text upto where confident 
%chunking has been performed. For example, in case of a continuous prediction there would be no change and since the 
%predicted tag of the new word corresponds to that already of the expanding chunk, this word is also included in the 
%same chunk. In case of a doubt, the flag is set at the same position, and no final decision on labelling the word is 
%performed, to have more confidence on the code-switch, the process moves on to the next token, if it corresponds to 
%that of the previous chunk, then both these undecided words are labelled and included in the chunk, otherwise a change 
%is noted and a new chunk is created with the changed label. In this process, we are trying to identify the sub-segments 
%that we need, thus performing both tasks at once, the first being language prediction and second being the chunking decision.

@@

This paper has presented a very preliminary investigation into subsegment language identification in Celtic language texts. We have
proposed a model that chunks input text into segments and performs language identification on these segments at the same time. Precision and
recall are low, leaving a lot of room for further work. Some of our plans are as follows. We would like to annotate more test data,
at least 100 tweets in each language. Although In \cite{king2013labeling}, the authors label on a per word level, yet we would like to include supervised methods and features talked about in this research to improve our efficiency while dealing with segments. We would also like to attempt our method using higher order character n-gram models for backoff, and n-gram word language models for detection.
